
\chapter{Literature Survey}

\section{Face Recognition}

\subsection{Background and Related Work}
Much of the work in computer recognition of faces have been approached by
characterizing a face by a set of geometric parameters and performing pattern
recognition based on the parameters. \\
Kanade's face identification system \cite{Kanade1973} was the first system in which all
steps of the recognition process were automated, using a top-down control strategy
directed by a generic model of expected feature characteristics. His system calculated
a set of facial parameters from a single face image and used a pattern classification
technique to match the face from a known set. This approach was a statistical
based approach, which depended primarily on local histogram analysis and absolute
gray-scale values. \\

\section{Voice Recognition}

\subsection{Background and Related Work}
Speaker recognition is the identification of the person who is speaking by
characteristics of their voices (voice biometrics), also called voice recognition. \\
Speech is a kind of complicated signal produced as a result of several transformations
occuring at different levels: semantic, linguistic and acoustic. Differences in these transformations may lead to differences in the acoustic properties of signals. The recognizability of speaker can be affected not only by the linguistic message but also the age, health, emotional state and effort level of the speaker. \\
Background noise and performance of recording device also interfere the classification process. \\
Speaker recognition is an important part of Human-Computer Interaction (HCI). As the trend of employing wearable computer reveals, Voice User Interface (VUI) has been a vital part of such computer. As these devicesare particularly small, they are more likely to lose and be stolen. In these scenarios, speaker recognition is not only a good HCI, but also a combination of seamless interaction with computer and security guard when the device is lost. The need of personal identity validation will become more acute in the future. Telephone banking and Telephone reservation services will develop rapidly when secure means of authentication are available. \\
